An empirical study of fixation for strategies in the Iterated Prisoner's Dilemma

### 2017-04-29 main.tex
Minor adjustments and run with new data.

    To the authors knowledge this is the largest
    such study. It allows for insights about the behaviour and
    performance of strategies with regard to their survival in an
    evolutionary setting.
\end{abstract}  % TODO Add main conclusion/finding.

@@

All strategies are paired and these pairs are used in 1000 repetitions of a
Moran process assuming a starting population of \((N/2, N/2)\). This is repeated
for even \(N\) between 2 and 14. The fixation probability is then estimated for
each value of \(N\).
% TODO The above is no longer true.

Note that due to the high computational cost of these experiments, for any given
interaction between two players within the Moran process the outcome is sampled
from a pre computed cache of 1000 match outcomes. This is carried out using an
software written for the purpose of this work. This has been
implemented in \cite{axelrodproject} ensuring that it can be used to either
reproduce the work or carry out further work.

@@

\begin{enumerate}
    \item The top strategy is an extortionate Zero determinant
        strategy~\cite{Press2012} with parameters \(l=1\) and \(s=1/4\).
    \item The Collective strategy has a simple handshake mechanism (a
        cooperation followed by a defection on the first move). As long as the
        opponent plays the same handshake and does not defect in the future it
        cooperates. Otherwise it defects for all rounds~\cite{Li2009}.  This
        strategy was specifically designed for Evolutionary processes so it is
        perhaps also not surprising that it does well here.
    \item The finite state machine stragegy % TODO Perhaps refer to earlier
        % discussion in the methodology section about these FSM strategies
    \item The Feld strategy is the corresponding strategy submitted to Axelrod's
        first tournament~\cite{Axelrod1980a}: it punishes defections but
        otherwise defects with a random probability that decays over time.
    \item The final strategy in the top five is another extortionate Zero
        determinant strategy~\cite{Press2012} with parameters \(l=p\).
\end{enumerate}

@@

>>>>

    To the authors knowledge this is the largest
    such study. It allows for insights about the behaviour and
    performance of strategies with regard to their survival in an
    evolutionary setting.

    Evidence is presented that shows that classical analysis of evolutionary
    dynamics with 2 individuals is misleading. Furthermore, it is shown that
    players with long memories and sophisticated behaviours outperform many
    strategies that perform well in a 2 individual setting (such as zero
    determinant strategies).

\end{abstract}

@@

All strategies are paired and these pairs are used in 1000 repetitions of a
Moran process assuming a starting population distribution of \(1, N-1 \),
\((N/2, N/2)\) and \(N-1 , 1\). This is repeated for \(N\) between 2 and 14. The
% TODO Change 14 to 12 if we do not use the 14 case.
fixation probability is then estimated for each value of \(N\).

Note that due to the high computational cost of these experiments, for any given
interaction between two players within the Moran process the outcome is sampled
from a pre computed cache of 1000 match outcomes. This is carried out using
software written for the purpose of this work. This has been
implemented in~\cite{axelrodproject} ensuring that it can be used to either
reproduce the work or carry out further work.
% TODO Perhaps write some pseudo code for this?

@@

\begin{enumerate}
    \item The top strategy is an extortionate Zero determinant
        strategy~\cite{Press2012} with parameters \(l=1\) and \(s=1/4\).
    \item The Collective strategy has a simple handshake mechanism (a
        cooperation followed by a defection on the first move). As long as the
        opponent plays the same handshake and does not defect in the future it
        cooperates. Otherwise it defects for all rounds~\cite{Li2009}.  This
        strategy was specifically designed for Evolutionary processes so it is
        perhaps also not surprising that it does well here.
    \item The finite state machine strategy % TODO Perhaps refer to earlier
        % discussion in the methodology section about these FSM strategies
    \item The Feld strategy is the corresponding strategy submitted to Axelrod's
        first tournament~\cite{Axelrod1980a}: it punishes defections but
        otherwise defects with a random probability that decays over time.
    \item The final strategy in the top five is another extortionate Zero
        determinant strategy~\cite{Press2012} with parameters \(l=p\).
\end{enumerate}

@@

% TODO I do not understand the narrative for this and what it adds to the paper.
